\documentclass{beamer}
\usetheme{Rochester}

\title[F3ildCrypt]{F3ildCrypt: End-to-End Protection of Sensitive Information
in Web Services}

\author[Burnside, Keromytis]{Matthew Burnside and Angelos D. Keromytis}

\institute[Columbia University]{
Department of Computer Science\\
Columbia University\\
\texttt{\{mb, angelos\}@cs.columbia.edu}
}
\date{ISC 2009}

\begin{document}

\begin{frame}[plain]
    \titlepage
\end{frame}

\begin{frame}
\frametitle{Motivation}
\begin{itemize}
\item Identity-related information is valuable
\item You must provide such information when using an online merchant
\item Can we protect this information end-to-end?
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Outline}
\tableofcontents
\end{frame}

\section{Introduction}

\begin{frame}
\frametitle{Introduction}
\begin{itemize}
\item Users have to trust online merchants:
\item Merchant is not malicious
\item Merchant site is maintained by diligent sysadmins
\item Merchant will protect always sensitive information
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{SOA Trust}
\begin{itemize}
\item In Service Oriented Architectures, have to trust:
\item Merchant \emph{and peer SOAs} are not malicious
\item Merchant \emph{and peer SOAs} are maintained by diligent sysadmins
\item Merchant \emph{and peer SOAs} will always protect sensitive information
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Data in Transit}
\begin{itemize}
\item In this work, we focus on data in transit
\item We protect the data from the web browser to the back-end database
\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Example}
\begin{itemize}
\item XXX: Diagram showing web browser, merchant, and SOA doing credit-card
transactions.  Even with SSL, only protected from web browser to merchant.
\end{itemize}
\end{frame}

\section{Related Work}


\begin{frame}
\frametitle{XACML}
Here is one slide.
\end{frame}

\begin{frame}
\frametitle{W3bCrypt}
Here is one slide.
\end{frame}

\section{Architecture}
\begin{frame}
\frametitle{Architecture}
Here is one slide.
\end{frame}

\begin{frame}
\frametitle{Proxy Re-Encryption}
Here is one slide.
\end{frame}

\section{Evaluation}
\begin{frame}
\frametitle{Evaluation}
Here is one slide.
\end{frame}

\section{Conclusion}
\begin{frame}
\frametitle{Conclusion}
Here is another slide.
\end{frame}

\end{document} 
